---
title: "Beyesian Analysis"
output: html_document
date: "2024-07-03"
---

First, we need to build a proximity matrix for the 63 countries, to include in the multilevel analysis to account for nonindependence between the countries used as predictor variables.  

1. Extracting the coordinates file for all counrties
```{r}
# From GitHub
url = "https://gist.githubusercontent.com/ofou/df09a6834a8421b4f376c875194915c9/raw/355eb56e164ddc3cd1a9467c524422cb674e71a9/country-capital-lat-long-population.csv"

raw_data = read.csv(url)
raw_data$Country = tolower(raw_data$Country)

head(raw_data)
```


2. Opening Mada's Predictor Data
```{r}
library(readxl)
pdata = read_excel("PredictorData.xlsx")

head(pdata)
```

3. Adding the Latitude and Longitude coordinates of all 63 countries as two columns from the online coordinates database. 
```{r}
library(dplyr)
library(openxlsx)
new_predictor = pdata %>% 
  left_join(raw_data, by = "Country")

# This data contains NA values for coordinates for a few countries, so we manually completed them. 
```

4. Open NewPredictor, the complete list of countries and their polar coordinates. 
```{r}
new_predictor = read_excel("NewPredictor.xlsx")
head(new_predictor)
# View(new_predictor)
```

5. Create the distance matrix
```{r}
library(dplyr)
library(geosphere)

countries = new_predictor$Country # Array of countries

# Array of latitudes in order of countries array + check to ensure their range is correct
latitudes = new_predictor$Latitude 
l_range = between(latitudes, -90, 90)
print(length(l_range))

# Array of longitudes in order of countries array + check to ensure their range is correct
longitudes = new_predictor$Longitude
lg_range = between(longitudes, -180, 180)
print(length(lg_range))

# Build data frame for geosphere's distm function. Note, all distances will be positive or 0. 
coordinates_df <- data.frame(longitude = longitudes, latitude = latitudes)
coordinates_matrix <- as.matrix(coordinates_df) 
distance_matrix <- distm(coordinates_matrix, fun = distGeo)

# print(distance_matrix)
```


6. Compute the geographic proximity matrix as 1 - [log(geographic distance matrix) scaled between 0 and 1].

```{r, warning=T}

# Test to ensure all distances are positive.
all_positive <- all(distance_matrix >= 0)

# Print the result
if (all_positive) {
  print("All entries in the matrix are positive.")
} else {
  print("Matrix contains non-positive entries.")
}


# Take log of non-zero entries
log_distances = distance_matrix # new matrix where the log is stored 
indices = which(log_distances != 0) # indices of nonzero enteries
log_distances[indices] = log(distance_matrix[indices])
# View(log_distances)


# Re-scaling between 0 and 1
mat_min = min(log_distances)
mat_max = max(log_distances)
rescaled_log_distances = (log_distances - mat_min)/(mat_max - mat_min)
# View(rescaled_log_distances)


# Final proximity matrix.
proximity_matrix <- 1 - rescaled_log_distances
colnames(proximity_matrix) = countries
rownames(proximity_matrix) = countries
head(proximity_matrix)
# View(proximity_matrix)
```


7. Beyesian Multilevel modelling

i. Belief
```{r}
library(brms)
library(lme4)
library(lmerTest)

data = read.csv("data.csv")
# View(data)


m_belief <- brm(
  BELIEFcc ~ Individualism + (1 | gr(Country, cov = proximity_matrix)), 
  data = data,
  data2 = list(proximity_matrix = proximity_matrix),
  family = gaussian()
  )

print(summary(m_belief))

plot(m_belief)
```


ii. Policy 
```{r}
m_policy = brm(
  POLICYcc ~ Individualism + (1 | gr(Country, cov = proximity_matrix)), 
  data = data,
  data2 = list(proximity_matrix = proximity_matrix),
  family = gaussian()
  )

print(summary(m_policy))
plot(m_policy)
```


iii. Share
```{r}

m_share = brm(
  SHAREcc ~ Individualism + (1 | gr(Country, cov = proximity_matrix)), 
  data = data,
  data2 = list(proximity_matrix = proximity_matrix),
  family = bernoulli("logit")
  )

print(summary(m_share))
plot(m_share)
```

iv. Wept 
```{r}
data$WEPTcc <- factor(
  data$WEPTcc, 
  levels = c(0, 1, 2, 3, 4, 5, 6, 7, 8),
  labels = c('Level0', 'Level1', 'Level2', 'Level3', 'Level4','Level5', 'Level6', 'Level7','Level8'),
  ordered = TRUE
)

m_wept = brm(
  WEPTcc ~ Individualism + (1 | gr(Country, cov = proximity_matrix)), 
  data = data,
  data2 = list(proximity_matrix = proximity_matrix),
  family = cumulative("logit")
  )

print(summary(m_wept))
plot(m_wept)

```














